\documentclass[letterpaper,10pt,draftclsnofoot,onecolumn]{IEEEtran}

\usepackage[margin=0.75in]{geometry}

\def\name{Kin-Ho Lam, Logan Wingard, Daniel Ross \group}
\def\team{Aerolyzer }
\def\assign{Problem Statement}
\def\group{(Group 19)}
\def\course{CS 461 Fall 2017}

% Title page
\title{\team \assign}
\author{\name}
\setlength{\parindent}{0pt}
\begin{document}
\maketitle
\vspace*{10em}
\centering
\course
\vspace*{4em}

\begin{abstract} 
Atmospheric aerosols are particles suspended in the atmosphere. These particles originate from natural sources such as volcanic eruptions, and unnatural sources such as fossil fuel combustion. One can visibly see the effects of aerosols in the 'Rayleigh scattering effect' which visibly reddens sunsets and sunrises. The Aerolyzer Project aims to deliver a new source of air quality and weather information through leveraging machine learning algorithms to characterize aerosol content in the atmosphere. When complete, this open-source project shall feature a python library that uses image classification and third-party weather APIs, displayed with an intuitive web-based user interface.
\end{abstract}

\clearpage
\begin{flushleft}
\section{Problem Definition}
Monitoring atmospheric aerosols is important; high concentrations directly and indirectly impact the atmosphere's chemical composition and radiation distribution. Ideally the atmosphere would be composed entirely of gases, but the presence of aerosols reduces air quality and extended exposure to aerosols can lead to health complications like bronchitis. Unfortunately, aerosols in the atmosphere are constantly changing, and current tools such as satellite, aircraft, and ground-based instruments do not compile data into language easily understandable by the average person. Currently, there is no way to judge local air quality using regional aerosol data without in-depth atmospheric knowledge. Additionally, delayed or inaccurate atmospheric reports complicate getting reliable local atmospheric information. 

\section{Proposed Solution}
The Aerolyzer project aims to estimate local air quality using regional weather data and aerosol analysis for users in the United States. This can be accomplished by crowd-sourcing cell phone images of the horizon, sunsets, and sunrises into a central database for analysis. The primary objective of this project is to create a python library that extracts location data from images and analyzes said images for aerosol content using the OpenCV library (an open source computer vision library). The secondary goal of the Aerolyzer project is to develop an application that collects images from users and delivers the python library in an intuitive web-based UI.
\par
The library shall be able to provide general weather data amassed from a public API regardless of whether the user provides an image or a zip code. The library  shall be capable of performing color analysis on images that have been classified as sunrises or sunsets to estimate aerosol content. Based on this color analysis, the application shall display the aerosol that most likely caused the hue distribution.
\par
The Aerolyzer web application has been partially developed and shall be expanded to present two options to the user: contribute to the Aerolyzer project by uploading their image of the horizon, or look up local air quality by zip code. The Aerolyzer project shall exclusively serve users in the United States. The Aerolyzer python library shall use image classification algorithms to filter out images that do not contain the horizon during sunrises or sunsets. Acceptable images shall be stored and categorized in a database for analysis. 

\section{Performance Metrics} 
The horizon is defined as the line at which the sky and earth's surface appear to meet. A sunrise is defined as the colors and light visible in the sky produced by the sun's first appearance in the morning. A sunset is defined as the colors and light visible in the sky produced when the sun disappears in the evening. These definitions are the criteria that the library’s classification functions will based on. The classification functions may utilizing OpenCV or other machine learning libraries for it’s image interpretation and machine learning functionality.
\par
When completed, this library shall identify horizons in a test-selection of images with a minimum accuracy of 50\% certainty. Images of horizons that contain sunsets and sunrises shall be identified with a minimum of 50\% certainty. This certainty shall be verifiable through a series of regression tests to prove the accuracy of horizon detection. Regression tests are defined as a set of pre-selected images which have an expected result (ex. Whether or not the image contains a horizon/sunset/sunrise). Passing a regression test is defined as fulfilling or matching the expected result. 
\par
When a user submits an image, the library will first determine if the image is classified as an acceptable image and then check if the image has valid EXIF metadata. If accepted, the image's zip code is identified via its longitude and latitude. Images will be categorized by zip code and then time for any future referencing. When a user requests information for a zip code, they will receive all the information relevant to that zip code that the library already had access to. In either user story, the python library will call on 3rd party weather APIs, including Wunderground, for their data on the relevant Zip Code.
\par
When a user submits an image, the library will first determine if the image has valid EXIF metadata and is an acceptable image. Acceptable EXIF metadata is defined by images that have valid location data and date/timestamp.  If accepted, the image's zip code is identified via its longitude and latitude. Acceptable images are defined as images of the horizon, sunset, or sunrise. The database shall categorize images by zip code. When a user requests information using a specific zip code, the Aerolyzer site shall display the most recent aerosol analysis relevant to their location. In either user story, the python library shall call on third-party weather APIs including Wunderground, for their data on the relevant zip Code.
\par
A submitted image's color profile shall analysed using OpenCV to or other machine learning systems to compare the hues to a predetermined data set which correlates certain colors with the presence of aerosols. Aerosols scatter light with a wavelength that is larger than its particle diameter, so the size of the particles can be inferred from the colors in the image. 
\par
To standardize development between different computers and operating systems, a virtual-machine development environment shall be created. This environment shall contain the libraries and tools necessary to run the Aerolyzer Python library as a stand-alone program as well as verify the aforementioned classifier certainty and regression tests.

\clearpage

\section*{Signatures}

\subsection*{Kim Whitehall}

\begin{tabular}{ l p{10pt} l }
Signature: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[5pt]
Date: && \hspace{0.5cm} \today
\end{tabular}

\subsection*{Kin-Ho Lam}

\begin{tabular}{ l p{10pt} l }
Signature: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Date: && \hspace{0.5cm} \today
\end{tabular}

\subsection*{Logan Wingard}

\begin{tabular}{ l p{10pt} l }
Signature: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Date: && \hspace{0.5cm} \today
\end{tabular}

\subsection*{Daniel Ross}

\begin{tabular}{ l p{10pt} l }
Signature: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Date: && \hspace{0.5cm} \today
\end{tabular}
\end{flushleft}
\end{document}